\documentclass[10pt, letterpaper, ragged2e, withhyper]{AltaCV/altacv}
%------------------------------------------------------------------------------
\usepackage[default]{lato}
\usepackage{paracol}

%------------------------------------------------------------------------------
%Variables to turn on and off sections and tailor
\def\Rohde{1}
\def\LMCO{1}

\def\RUWPTRX{0}		%WPTRx Research project
\def\RUSDR{1}		%SDR Project in Modern Communications systems
\def\RUXILINX{0}	%Xilinx accelerator using Vivado
\def\RSEAMP{0}		%R&S Amplifier controller
\def\RSDATA{1}		%Data scraping project at Rohde
\def\CSMBLDC{1}		%CMS Senior Design Project
\def\CSMQUAD{0}		%Quad Copter Project
\def\LSROBO{0}		%Robot arm project for engineering class
\def\FTCROBO{0}		%Robot for the FTC challenge

%------------------------------------------------------------------------------
% Colors for Document4
\definecolor{VividPurple}{HTML}{3E0097}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}

\definecolor{P2RLGrey}{HTML}{e1e1e1}
\definecolor{P2ROrange}{HTML}{f5ae23}
\definecolor{P2RLBlue}{HTML}{9ca2c4}
\definecolor{P2RBlue}{HTML}{4a6084}
\definecolor{P2RGrey}{HTML}{d1d4dd}

%------------------------------------------------------------------------------
%Assign Colors to the appropriate styles
%\colorlet{heading}{VividPurple}
%\colorlet{headingrule}{VividPurple}
%\colorlet{accent}{VividPurple}
%\colorlet{emphasis}{SlateGrey}
%\colorlet{body}{LightGrey}
%\colorlet{tagline}{SlateGrey}

\colorlet{name}{SlateGrey}
\colorlet{heading}{P2RBlue}
\colorlet{headingrule}{P2RBlue}
\colorlet{accent}{black}
\colorlet{emphasis}{P2RBlue}
\colorlet{body}{SlateGrey}
\colorlet{tagline}{P2RLBlue}
\colorlet{subheading}{P2RLBlue}


%------------------------------------------------------------------------------
%Change the bullets for itemize and rating marker
\renewcommand{\cvItemMarker}{{\small\textbullet}}
\renewcommand{\cvRatingMarker}{\faCircle}

%------------------------------------------------------------------------------
\begin{document}

%------------------------------------------------------------------------------
\name{Cameron Kramr}
\tagline{RF \& Embedded Electrical Engineer}

\personalinfo{
	\phone{832-370-8131}
	\email{CameronKramr@gmail.com}
	\github{CameronKramr}
	\mailaddress{Houston Tx, 77043}
	\linkedin{CameronKramr}
}

\makecvheader

%------------------------------------------------------------------------------
%Change itemized things to be slightly smaller
\AtBeginEnvironment{itemize}{\normalsize}
%Configure Column Ratio to be pleasing
\columnratio{0.6}

\begin{paracol}{2}

%------------------------------------------------------------------------------
\cvsection{Prior Projects}

\if\RUWPTRX1
\cvevent{Wireless Power Receiver}{Rice University, Research Project}{Jan. 2023 - Jul. 2023}{}
\begin{itemize}
\item Designed \& assembled PCB for fine-pitch BGA components
\item Developed bare-metal C drivers for QI chip over I2C
\item Developed ncurses GUI for HUD over UART 
\end{itemize}
\fi

\if\RUSDR1

\if\RUWPTRX1
\divider
\fi

\cvevent{Software Defined Radio (SDR) Transceiver}{Rice University, Modern Communications Course}{Aug. 2022 - Dec. 2022}{}
\begin{itemize}
\item Developed SDR algorithm to send \& receive data wirelessly
\item Implemented simplified Wifi stack
\item Implemented QAM, BPSK, DQPSK, \& other modulation techniques
\end{itemize}
\fi


\if\RUXILINX1

\divider

\cvevent{Systolic Matrix Decomposition Accelerator}{Rice University, Advanced Digital Design Course}{Aug. 2022 - Dec. 2022}{}
\begin{itemize}
\item Developed IP blocks using Xilinx Vivado workflow
\item Solved for matrix inverse using QR Decomposition
\item Implemented Given's rotation using custom CORDIC modules
\end{itemize}
\fi

\if\RSEAMP1
\divider
\cvevent{Embedded Amplifier Controller}{Rohde \& Schwarz}{Nov. 2021 - May. 2022}{}
\begin{itemize}
\item Programmed custom task scheduler on AVR platform
\item Implemented HTML server
\item Implemented industry standard remote protocol over TCP
\item Collaborated with co-workers using GIT
\end{itemize}
\fi

\if\RSDATA1

\divider

\cvevent{Data Scraper}{Rohde \& Schwarz}{Dec. 2021 - Feb. 2022}{}
\begin{itemize}
\item Built tool in python to extract data from dirty source
\item Analyzed over 20,000 lines of dirty Excel data in python
\item Used insights from data to improve project designs
\end{itemize}
\fi

\if\CSMBLDC1
\divider
\cvevent{BLDC Motor Controller}{Colorado School of Mines, Capstone Project}{Jan. 2020 - Dec. 2020}{}
\begin{itemize}
\item Designed \& tested multiple custom PCBs
\item Wrote SV-PWM motor controller in embedded C
\item Implemented EMF position detection using ADCs \& DMA 
\end{itemize}
\fi

\if\CSMQUAD1
\divider
\cvevent{Quad Copter Project}{Colorado School of Mines, Embedded Systems Course}{Aug. 2019 - Dec. 2019}{}
\begin{itemize}
\item Designed \& fabricated custom PCB in Eagle
\item Implemented wireless UART link
\item Developed embedded C drivers for MMU over SPI on PIC platform
\end{itemize}
\fi


\if\LSROBO1
\divider

\cvevent{Robot Arm}{Lone Star College, Introduction to Engineering}{Jan. 2017 - May. 2017}{}
\begin{itemize}
\item Designed \& built 3D printed robot arm
\item Implemented reverse kinematics to enable position control
\item Implemented advanced controller in C++ to enable real-time control
\end{itemize}
\fi


\if\FTCROBO1

\divider

\cvevent{First Tech Challenge (FTC) Competition}{Team Atlas}{Aug. 2015 - May. 2016}{}
\begin{itemize}
\item Organized team to compete in the FTC competition
\item Fabricated design using CNC machine
\item Designed robot in Autodesk Inventor
\end{itemize}
\fi

%Experience template
\iffalse

\divider

\cvevent{Project name}{Where \& for what}{Aug. 20XX - Dec. 20XX}{}
\begin{itemize}
\item First
\item Second
\item Last
\end{itemize}
\fi

%------------------------------------------------------------------------------
\cvsection{Employment History}

\if\Rohde1
\cvevent{Systems Architect} {Rohde \& Schwarz}{Mar. 2021 -- Aug. 2022 -- Dallas, TX.}{}
\begin{itemize}
\item Developed projects post-sales from design to delivery to training
\item Conducted design reviews for customer approval
\item Supported teammates for flexible resource deployment
\end{itemize}
\divider
\fi

\if\LMCO1
\cvevent{RF Design Intern}{Lockheed Martin RF Center of Excellence}{Jun. 2020 -- Aug. 2020 -- Littleton, CO.} {}
\begin{itemize}
\item Applied RF principles to design devices
\item Verify designs in simulation \& present results to team
\end{itemize}
\fi

%------------------------------------------------------------------------------
\switchcolumn

%------------------------------------------------------------------------------
\cvsection{Education}
\cvevent{M.S. Electrical Engineering} {Rice University}{Aug. 2022 -- Dec. 2023 -- GPA 3.6}{}

%\newline
\divider

\cvevent{B.S. Electrical Engineering} {Colorado School of Mines}{Aug. 2018 -- Dec. 2020 -- GPA 3.7}{}
\divider

\cvevent{Associates of Science} {Lone Star College}{Aug. 2015 -- May. 2018 -- GPA 4.0}{}
\divider

\cvevent{Associates of Arts} {Lone Star College}{Aug. 2015 -- May. 2018 -- GPA 4.0}{}

%------------------------------------------------------------------------------
\iffalse
\cvsection{Soft Skills}

\cvskill{Written communication}{4.5}
%\cvskill{Workflow Improvement}{4.5}
\cvskill{Team work}{4}
%\cvskill{Customer Focus}{4}
\cvskill{Agile}{2.5}
\fi
%------------------------------------------------------------------------------
\cvsection{Skills}

\cvsubsection{Electrical Skills}
\cvtag{AVR}
\cvtag{PIC}
\cvtag{ARM}
\cvtag{Spice}
\cvtag{RF Design}
\cvtag{PCB Assembly}
\cvtag{Hand Soldering}
\cvtag{Debugging}

~\\
\cvsubsection{Computer Skills}
\cvtag{C}
\cvtag{C++}
\cvtag{Python}
\cvtag{Lua}
\cvtag{Linux}
\cvtag{GNUMake}
\cvtag{\LaTeX}
\cvtag{GIT}
\cvtag{MS Office}

~\\
\cvsubsection{Design Skills}
\cvtag{KiCAD}
\cvtag{MS Visio}
\cvtag{AutoCAD}
\cvtag{Ansys}
\cvtag{HFSS}
\cvtag{Maxwell 3D}

\cvsection{Achievements}
\cvachievement{\faGraduationCap}{Deans List Student}{Colorado School of Mines}
\cvachievement{\faGraduationCap}{Deans List Student}{Lone Star College}
\cvachievement{\faTrophy}{Eagle Scout}{}

\end{paracol}

\end{document}
